LAGOS lake depth

### 2020-12-07 manuscript/si_template_2019.tex
round geometry metrics to two decimal places

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4820 (17700)\\
\textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4820 (17700)\\
\textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4820 (17700)\\
\textbf{Perimeter (m)} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4820 (17700)\\
\textbf{Shoreline development} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4820 (17700)\\
\textbf{Elevation (m)} & 300 (340) & 180 (210) & 400 (460) & 4820 (17700)\\
\textbf{Watershed-lake ratio} & 7.8 (10) & 3.8 (4.4) & 17 (29) & 4820 (17700)\\
\textbf{Deepest point distance (m)} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
Mean deepest point distance (m) & 140 (-) & 87 (-) & 230 (-) & 4820 (-)\\
\textbf{Visual center distance (m)} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
Inlake slope (m/m) & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4820 (-)\\
Inlake slope online (m/m) & 0.062 (-) & 0.029 (-) & 0.14 (-) & 4800 (-)\\
Inlake slopes (m/m) & 0.057 (-) & 0.032 (-) & 0.098 (-) & 4820 (-)\\
Inlake slopes online (m/m) & 0.07 (-) & 0.034 (-) & 0.15 (-) & 4800 (-)\\
Mean inlake slope (m/m) & 0.043 (-) & 0.021 (-) & 0.09 (-) & 4820 (-)\\
Nearshore mean slope (m/m) & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4820 (-)\\
Nearshore slope online (m/m) & 0.077 (-) & 0.038 (-) & 0.13 (-) & 4590 (-)\\
Nearshore slopes online (m/m) & 0.077 (-) & 0.037 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}

>>>>

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4820 (17700)\\
\textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4820 (17700)\\
\textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4820 (17700)\\
\textbf{Perimeter (m)} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4820 (17700)\\
\textbf{Shoreline development} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4820 (17700)\\
\textbf{Elevation (m)} & 300 (340) & 180 (210) & 400 (460) & 4820 (17700)\\
\textbf{Watershed-lake ratio} & 7.8 (10) & 3.8 (4.4) & 17 (29) & 4820 (17700)\\
\textbf{Deepest point distance (m)} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
Mean deepest point distance (m) & 140 (-) & 87 (-) & 230 (-) & 4820 (-)\\
\textbf{Visual center distance (m)} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
Inlake slope (m/m) & 0.05 (-) & 0.02 (-) & 0.08 (-) & 4820 (-)\\
Inlake slope online (m/m) & 0.06 (-) & 0.03 (-) & 0.14 (-) & 4800 (-)\\
Inlake slopes (m/m) & 0.06 (-) & 0.03 (-) & 0.1 (-) & 4820 (-)\\
Inlake slopes online (m/m) & 0.07 (-) & 0.03 (-) & 0.15 (-) & 4800 (-)\\
Mean inlake slope (m/m) & 0.04 (-) & 0.02 (-) & 0.09 (-) & 4820 (-)\\
Nearshore mean slope (m/m) & 0.08 (-) & 0.05 (-) & 0.11 (-) & 4820 (-)\\
Nearshore slope online (m/m) & 0.08 (-) & 0.04 (-) & 0.13 (-) & 4590 (-)\\
Nearshore slopes online (m/m) & 0.08 (-) & 0.04 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}

### 2020-12-07 tables/01_predictors.Rmd
round geometry metrics to two decimal places

# compute stats for bathymetry lakes
dt_bathy <- compute_stats(dt_bathy)
dt_bathy <- data.frame(dt_bathy)
# compute stats for all of lagosus
dt_all <- data.frame(compute_stats(dt_all))
dt_all <- dplyr::filter(dt_all, variable %in% dt_bathy$variable) 
# interleave
dt_combined <- suppressMessages(
  bind_cols(lapply(names(dt_bathy)[2:5], 
                           function(i) paste0(dt_bathy[,i], 
                                              " (", dt_all[,i], ")")))
  ) %>%
  setNames(names(dt_bathy)[2:5])

>>>>

# compute stats for bathymetry lakes
dt_bathy <- compute_stats(dt_bathy)
dt_bathy <- data.frame(dt_bathy)
# round geometry measures to two decimal points
clean_geometry <- function(x) as.character(round(as.numeric(x), 2))
dt_bathy$Median[which(dt_bathy$variable == "inlake_slope_pnt"):nrow(dt_bathy)] <-
  clean_geometry(
    dt_bathy$Median[which(dt_bathy$variable == "inlake_slope_pnt"):nrow(dt_bathy)])
dt_bathy$Q25[which(dt_bathy$variable == "inlake_slope_pnt"):nrow(dt_bathy)] <-
  clean_geometry(
    dt_bathy$Q25[which(dt_bathy$variable == "inlake_slope_pnt"):nrow(dt_bathy)])
dt_bathy$Q75[which(dt_bathy$variable == "inlake_slope_pnt"):nrow(dt_bathy)] <-
  clean_geometry(
    dt_bathy$Q75[which(dt_bathy$variable == "inlake_slope_pnt"):nrow(dt_bathy)])

# compute stats for all of lagosus
dt_all <- data.frame(compute_stats(dt_all))
dt_all <- dplyr::filter(dt_all, variable %in% dt_bathy$variable)

# interleave
dt_combined <- suppressMessages(
  bind_cols(lapply(names(dt_bathy)[2:5], 
                           function(i) paste0(dt_bathy[,i], 
                                              " (", dt_all[,i], ")")))
  ) %>%
  setNames(names(dt_bathy)[2:5])
